Towards Explainability of Machine Learning Models in Insurance Pricing

### 2019-11-01 manuscript/manuscript.Rmd
qualify mas exams as being cas exams

Arguably, GLMs predate minimum bias procedures by a significant margin. The term 
was coined by @nelder_wedderburn_1972, but generalizations of least squares 
linear regression date back at least to the 1930s. Like minimum bias methods, 
GLMs did not become mainstream in actuarial science for some time. For example, 
the syllabus of basic education of the Casualty Actuarial Society does not seem to include any mention of GLMs 
prior to @brown_1988 in the 1990 syllabus. From there, GLMs 
seem to have received only passing mention until 2006 with the introduction of 
@anderson_2005 to the syllabus.

@@

Paralelling the development of GLM was the development of machine learning 
algorithms throughout the middle part of the 20th century. Detailed histories 
of machine learning may be found in sources such as @nilsson_2009 and 
@wang_raj_2017. Consistent with GLMs, machine learning was relatively unpopular 
in actuarial science until the last ten years as computing power has become cheaper
and more easily available and as machine learning software packages have obviated
the need for developing analyses from scratch each time an analysis is performed.
Due to the breadth of machine learning as a field, it is difficult to identify 
the first time it entered the CAS syllabus; however, cluster analysis (in the 
form of k-means) seems to have been first included in 2011 with @robertson_2009.
More recently, the MAS-I and MAS-II exams introduced in 2018 have included 
machine learning explicitly.

@@

Within the actuarial profession, Actuarial Standard of Practice 41 ("Actuarial 
Communications") notes that "...another actuary qualified in the same practice 
area [should be able to] make an objective appraisal of the reasonableness of 
the actuary's work as presented in the actuarial report." [@asop_41] Underlying 
this requirement is an assumption that the hypothetical other actuary qualified 
in the same practice area is adequately familiar with the relevant techniques 
employed. Although the syllabus of basic education is constantly changing, there
has at times been an assumption that all techniques and assumptions that have 
ever been a part of the syllabus of basic education needn't be explained from 
first principles in general actuarial communications, and that an actuary 
practicing in the same field should be able to make an objective appraisal of 
the results from the methods found in the syllabus.
This is notable because, beginning with the introduction
of the MAS-I and MAS-II examination in July of 2018, several machine learning 
models were formally included in the syllabus of basic education. These exams 
cover a wide range of topics, such as splines, clustering algorithms, decision 
trees, boosting, and principle components analysis [@cas_syllabus_2018].

>>>>

Arguably, GLMs predate minimum bias procedures by a significant margin. The term 
was coined by @nelder_wedderburn_1972, but generalizations of least squares 
linear regression date back at least to the 1930s. Like minimum bias methods, 
GLMs did not become mainstream in actuarial science for some time. For example, 
the syllabus of basic education of the Casualty Actuarial Society (CAS) does not 
seem to include any mention of GLMs 
prior to @brown_1988 in the 1990 syllabus. From there, GLMs 
seem to have received only passing mention until 2006 with the introduction of 
@anderson_2005 to the syllabus.

@@

Paralelling the development of GLM was the development of machine learning 
algorithms throughout the middle part of the 20th century. Detailed histories 
of machine learning may be found in sources such as @nilsson_2009 and 
@wang_raj_2017. Consistent with GLMs, machine learning was relatively unpopular 
in actuarial science until the last ten years as computing power has become cheaper
and more easily available and as machine learning software packages have obviated
the need for developing analyses from scratch each time an analysis is performed.
Due to the breadth of machine learning as a field, it is difficult to identify 
the first time it entered the CAS syllabus; however, cluster analysis (in the 
form of k-means) seems to have been first included in 2011 with @robertson_2009.
More recently, the CAS MAS-I and MAS-II exams introduced in 2018 have included 
machine learning explicitly.

@@

Within the actuarial profession, Actuarial Standard of Practice 41 ("Actuarial 
Communications") notes that "...another actuary qualified in the same practice 
area [should be able to] make an objective appraisal of the reasonableness of 
the actuary's work as presented in the actuarial report." [@asop_41] Underlying 
this requirement is an assumption that the hypothetical other actuary qualified 
in the same practice area is adequately familiar with the relevant techniques 
employed. Although the syllabus of basic education is constantly changing, there
has at times been an assumption that all techniques and assumptions that have 
ever been a part of the syllabus of basic education needn't be explained from 
first principles in general actuarial communications, and that an actuary 
practicing in the same field should be able to make an objective appraisal of 
the results from the methods found in the syllabus.
This is notable because, beginning with the introduction
of the CAS MAS-I and MAS-II examination in July of 2018, several machine learning 
models were formally included in the syllabus of basic education. These exams 
cover a wide range of topics, such as splines, clustering algorithms, decision 
trees, boosting, and principle components analysis [@cas_syllabus_2018].
